True versus apparent shapes of astrophysical bow shocks

### 2015-06-29 papers/Paper1/sec-conic.tex
Fix some math-mode errors
Move emacs local variable section to end of file
Add short title and author list
Also, define commands for the cos/cosh terms in the conic section
equations.  Try out using cursive upper case letters, but we may change
those later
29/06/15 Some advances in conic section.
At this point there might be some mathematical inconsistencies, but still working on it

@@

\begin{align}
x = au_c(t)-x_0 \\ 
y = bv_c(t)
\end{align}

where:
\begin{align}
u_c(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~mathrm{if~hyperbola}
\end{array}\right
\end{align}\\
v_c(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~mathrm{if~hyperbola}
\end{array}\right \\
-\pi < t < \pi \\
R_0 = a - x_0 
\end{align}

@@

\begin{align}
x = au_c(t)-x_0 \\ 
y = bv_c(t)\cos\phi \\
z =  bv_c(t)\sin\phi
\end{align}

@@

\begin{align}
\tan\phi &= \frac{b}{a}w_c(t) 
\end{align}
where:

\begin{align}
w_c(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
-\coth t ~mathrm{if~hyperbola}
\end{array}\right
\end{align}
\subsection{Characteristic radii}

>>>>

\newcommand\Sin{\ensuremath{\mathcal{S}}}
\newcommand\Cos{\ensuremath{\mathcal{C}}}
\newcommand\Cot{\ensuremath{\mathcal{T}}}

@@

\begin{align}
x = a\Cos(t)-x_0 \\ 
y = b\Sin(t)
\end{align}

where:
\begin{align}
\Cos(t) = \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) = \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi < t < \pi \\
R_0 = a - x_0 
\end{align}

@@

\begin{align}
x = a\Cos(t)-x_0 \\ 
y = b\Sin(t)\cos\phi \\
z =  b\Sin(t)\sin\phi
\end{align}

@@

\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:

\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
-\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

We could work in another frame   where the origin is located at the conic's center: $(X,Y)$, where $X=x-X_0$ and $Y=y$.

In this frame,  we use the transformations (\ref{eq:Trans})  to obtain the apparent shape of the shell:

\begin{align}
X' = \frac{\Cos(t)}{a\cos i}\left(a^2\cos^2 i \pm b^2\sin^2 i\right)  \label{eq:conic-projected-x}\\
Y'= b\Sin(t)\left(1-\frac{b^2}{a^2}\tan^2 i\Cot(t)\right)^{1/2}
\label{eq:conic-projected-y}
\end{align}

We must show that the apparent shape of the shell in the observer's frame is still the same conic. To do that, we can write equations
(\ref{eq:conic-projected-x}) and (\ref{eq:conic-projected-y}) as follows:

\begin{align}
X' = a'\Cos t' \label{eq:conic-projected-x-2} \\
Y' = b'\Sin t' \label{eq:conic-projected-y-2}
\end{align}

Comparing, (\ref{eq:conic-projected-x}), (\ref{eq:conic-projected-x-2}), (\ref{eq:conic-projected-y}) and (\ref{eq:conic-projected-y}) we find that

\begin{align}
a' = a^2\cos^2 i \pm b^2\sin^2 i \\
\Cos t' = \frac{\Cos(t)}{a\cos i} \\
b' = b
\end{align}

Which proves that effectively the projection of a given conic is the same conic. With this knowledge, we can obtain the characteristic radii in
the observer's frame.

The minimum value of $t$ is such that $1-\frac{b^2}{a^2}\tan^2 i T^2(t_\parallel) =0$, where:

\begin{align}
X'(t_\parallel) = R'_0 \\
\Cot t = \frac{a^2}{b^2}\tan i
\end{align}
